Gravitational wave sources in our Galactic backyard: Predictions for BH and NS binaries in LISA

### 2021-07-11 paper/tex/sections/results.tex
add placeholder plot

\todo{There will also be a little bit more text to explain the example distribution over galaxies in the latter three panels -- will make once Floor combines the latest fiducial simulation data}

\begin{figure}[t]
    \centering
    \includegraphics[width=\columnwidth]{detectable_distance_distribution_4yr.pdf}
    \includegraphics[width=5.5cm, height=4.5cm]{example-image-a}
    \includegraphics[width=5.5cm, height=4.5cm]{example-image-a}
    \includegraphics[width=5.5cm, height=4.5cm]{example-image-a}
    \caption{\textbf{First panel:} As Figure~\ref{fig:fiducial_pdf_distributions}, but for the luminosity distance. \textbf{Final three panels:} A face-on view of an example Milky Way galaxy, where each point is coloured by its metallicity. Stars represent an example of the detectable systems in a 4-year LISA mission. Each panel corresponds to a separate DCO type. \todo{make plots}}
    \label{fig:detectable_distance_dist}
\end{figure}

>>>>

\todo{There will also be a little bit more text to explain the example distribution over galaxies in the lower panel -- will make properly once Floor combines the latest fiducial simulation data (this plot is sampling uniformly rather than based on the distribution)}

\begin{figure}[thb]
    \centering
    \includegraphics[width=\columnwidth]{detectable_distance_distribution_4yr.pdf}
    \includegraphics[width=\columnwidth]{sources_on_mw.png}
    \caption{\textbf{Top:} As Figure~\ref{fig:fiducial_pdf_distributions}, but for the luminosity distance. \textbf{Bottom:} A face-on view of an example Milky Way galaxy, where each point is coloured by its metallicity. The large $\odot$ shows the position of the Sun. Stars represent a typical example of the detectable systems in a 4-year LISA mission. \todo{make proper plot, maybe separate panels for different types (hard to arange then though), thoughts on black background?}}
    \label{fig:detectable_distance_dist}
\end{figure}
